Metadata collation

### 2025-05-17 metadata/parametadata_control.Rmd
Dropping wonky nitrate data and correcting Arg timepoint

```{r}
samp_filedata <- "mzMLs" %>%
  list.files(pattern = "Smp.*mzML", recursive = TRUE, full.names = TRUE) %>% 
  data.frame(filepath=.) %>%
  mutate(filename=basename(filepath)) %>%
  mutate(shortname=str_remove(filename, "-wIS|-noIS-neg|-noIS-pos")) %>%
  mutate(shortname=str_remove(shortname, ".*_Smp_")) %>%
  mutate(shortname=str_remove(shortname, ".mzML$")) %>%
  mutate(samp_type=ifelse(str_detect(shortname, "Blk"), "Blk", "Smp")) %>%
  mutate(IS_type=str_extract(filepath, "wIS|noIS")) %>%
  mutate(polarity=str_extract(filepath, "neg|pos")) %>%
  mutate(amendment=str_extract(shortname, "Nit|Amm|Arg|GMP")) %>%
  mutate(depth=str_extract(shortname, "Deep|Surf")) %>%
  mutate(startime=str_extract(shortname, "Eve|Morn")) %>%
  mutate(timepoint=str_extract(shortname, "T\\d+")) %>%
  mutate(timepoint_num=as.numeric(str_remove(timepoint, "T"))) %>%
  mutate(tripl=str_extract(shortname, "[A-C]$")) %>%
  mutate(untripl=str_remove(shortname, "-[A-C]$"))

>>>>

```{r}
samp_filedata <- "mzMLs" %>%
  list.files(pattern = "Smp.*mzML", recursive = TRUE, full.names = TRUE) %>% 
  data.frame(filepath=.) %>%
  mutate(filename=basename(filepath)) %>%
  mutate(shortname=str_remove(filename, "-wIS|-noIS-neg|-noIS-pos")) %>%
  mutate(shortname=str_remove(shortname, ".*_Smp_")) %>%
  mutate(shortname=str_remove(shortname, ".mzML$")) %>%
  mutate(samp_type=ifelse(str_detect(shortname, "Blk"), "Blk", "Smp")) %>%
  mutate(IS_type=str_extract(filepath, "wIS|noIS")) %>%
  mutate(polarity=str_extract(filepath, "neg|pos")) %>%
  mutate(amendment=str_extract(shortname, "Nit|Amm|Arg|GMP")) %>%
  mutate(depth=str_extract(shortname, "Deep|Surf")) %>%
  mutate(startime=str_extract(shortname, "Eve|Morn")) %>%
  mutate(timepoint=str_extract(shortname, "T\\d+")) %>%
  mutate(timepoint=case_when(
    amendment=="Arg" & depth=="Surf" & startime=="Eve" & timepoint=="T3"~"T18"
  )) %>%
  mutate(timepoint_num=as.numeric(str_remove(timepoint, "T"))) %>%
  mutate(tripl=str_extract(shortname, "[A-C]$")) %>%
  mutate(untripl=str_remove(shortname, "-[A-C]$")) %>%
  mutate(samp_type=case_when(
    amendment=="Nit" & depth=="Deep" & startime=="Eve" & timepoint=="T10"~"Bad"
  ))
